---
title: "CodeClan Day 2 Homework"
output: html_notebook
---


## 1. Part 1

1. Create a vector called `stock_prices` with the following data points: 23, 27, 23, 21, 34, 24, 25, 30, 37, 30.
```{r}
stock_prices <- c(23, 27, 23, 21, 34, 24, 25, 30, 37, 30)
```
 
 
1. Create a vector called `day_of_week`, which repeats Monday to Friday twice. i.e. ‘Monday’, ‘Tuesday’, ‘Wednesday’, ‘Thursday’, ‘Friday’, ‘Monday’, ‘Tuesday’, ‘Wednesday’, ‘Thursday’, ‘Friday’.
```{r}
day_of_week <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
```
 
 
2. Create a vector called `day_of_week_factor`, which has the same data as `day_of_week`, but as a factor.
```{r}
day_of_week_factor <- factor(day_of_week, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"), ordered = TRUE)
```
 
 
2. Created a vector called `named_stock_prices`, which is stock prices, named with days of the week.
```{r}
names(stock_prices) <- day_of_week
named_stock_prices <- stock_prices
named_stock_prices
```
 
 
3. Make a data frame called `stock_data` with the stock price and day of the week information in it, and View the result.
```{r}
stock_data <- data.frame(stock_prices, day_of_week_factor)
class (stock_data)
stock_data
```
 
 
4. Make a matrix called `stock_matrix` with 2 columns and 5 rows, so that the stock prices for one week are the first column, and the stock prices for the second week are the second column.
```{r}
stock_matrix <- matrix(stock_prices, byrow = FALSE, nrow = 5)
stock_matrix
```
 
 
5. Make a list called `stock_list` with named elements, that has the individual vectors of `stock_prices` and `day_of_week` along with the matrix you made in question 4.
```{r}
stock_list <- list(stock_prices, day_of_week, stock_matrix)
stock_list
```
 
 
## 2. Part 2 

1. Select the 4th, 5th and 6th stock prices from `stock_prices`.
```{r}
stock_prices[c(4, 5, 6)]
```


1. Select the stock prices greater than 30 from `stock_prices`.
```{r}
stock_prices[stock_prices > 30]
```

2. Select the `day_of_week` column from the `stock_data` data frame.
```{r}
stock_data[, 2]
```


2. Select the rows of the `stock_data` data frame where the `stock_prices` is less than 25.
```{r}
subset(stock_data, subset = stock_prices < 25)
```

3. Select the 1st column of the matrix
```{r}
stock_matrix[, 1]
```


3. Select the 3rd row of the matrix
```{r}
stock_matrix[3, ]
```


3. Select the 3rd element in the 1st row of the matrix *(should this be 3rd element in the 1st column?)*
```{r}
stock_matrix[3, 1]
```

4. Select the matrix stock_matrix from `stock_list`.
```{r}
stock_list[[3]]
```

## 3. Extension

Download the `tidyquant` library.

Use it to get stock prices from a company of your choice from the current year. You’ll need to look up the help file to do this.

Edit the data frame so only columns are date and closing.

Subset to find the rows where closing price is higher than average.

```{r include=FALSE}
install.packages("tidyquant")
```

```{r include=FALSE}
library(tidyquant)
```

Investigating help.
```{r}
browseVignettes(package = "tidyquant")
```

```{r}
tq_index_options()
```

```{r}
tq_index("DOW")
```

Edit the data frame so only columns are date and closing.
```{r}
GS_prices  <- tq_get("GS", get = "stock.prices", from = " 2019-01-01")
str(GS_prices)
keeps <- c("date", "close")
GS_prices_two_columns <- GS_prices[keeps]
GS_prices_two_columns
```

```{r}
mean(GS_prices_two_columns$close)
```

Subset to find the rows where closing price is higher than average.
```{r}
subset(GS_prices_two_columns, subset = GS_prices_two_columns$close > mean(GS_prices_two_columns$close))
```







